### 2023-01-19 README.Rmd

```{r fairfield}
fairfield_age_pop <- abs_age_lga("Fairfield (C)")
fairfield_age_pop
```

@@

```{r predict-contacts}
set.seed(2022 - 09 - 06)
synthetic_contact_fairfield <- predict_contacts(
  model = contact_model,
  population = fairfield_age_pop,
  age_breaks = c(seq(0, 85, by = 5), Inf)
)

>>>>

```{r fairfield}
fairfield <- abs_age_lga("Fairfield (C)")
fairfield
```

@@

```{r predict-contacts}
set.seed(2022 - 09 - 06)
synthetic_contact_fairfield <- predict_contacts(
  model = contact_model,
  population = fairfield,
  age_breaks = c(seq(0, 85, by = 5), Inf)
)
